Learning constraints in spreadsheets and tabular data

### 2016-05-28 Paper/ECAI/tabular.tex
WIP working on comments

\begin{table*}
\caption{
  Overview of constraint templates implemented in \sname.
  Templates marked with $\dagger$ are \textit{aggregate} templates, the table shows the version for sum but \sname also supports max, min, average, product and count.
  Subgroups in normal font have to be vectors, whereas subgroups in \textbf{bold} may contain more than one vector.
  Templates marked with $*$ are \textit{structural}, i.e. they are not functional and cannot be implemented in most spreadsheet software.
  $\discrete(x)$ is a shortcut for: $\textual(x) \lor \numeric(x)$.
}\label{table:constraints}
  {\centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ \hline \hline
    $\ecalldiff{\sg_x}^*$
      & $\discrete(\sg_x)$

@@

  \luc{there are some fancy constraints here. it might be good to say something about them ... like an example of one of the more complex ones in the text ... maybe state what conditional means, what aggregate ... }
\end{table*}

@@

  \item \CSignature: $\sg_r$ has to be a single vector ($\textit{size}=1$) while $\mathbf{\sg_x}$ can be a block ($\textit{size}>=1$), which can be derived from the use of a normal or \textbf{bold} font. The two blocks have to be numeric. This constraint is orientation-specific, so it requires that the number of rows in $\mathbf{\sg_x}$ equals the length of $\sg_r$. While not strictly needed, we also add to the bias of this template that the number of columns to sum over is larger than $2$ as a block with two columns will also be captured by the $\eccalc{\sg_r}{\sg_1 + \sg_2}$ constraint; \samuel{check}

@@

\subsubsection{Redundancies}
\label{sec:form:redundancies}
Depending on the application, some constraints in the solution to the tabular constraint learning problem may be considered \textit{redundant}. This is because constraints may be logically equivalent or may be implied by other constraints.

\luc{if you have permutation, alldiff is redundant.}

@@

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint template all valid argument assignments in two steps:
\begin{enumerate}
\item For each constraint template~$s$, generate all assignments $(B_1, \ldots ,B_n)$ where each $B_i$ is a superblock and the $B_i$ are \textit{compatible} (defined below) with the signature of~$s$. 
\item For each generated assignment $(B_1, \ldots ,B_n)$ in 3a), find all valid constraints $s(B'_1, \ldots, B'_n)$ such that for all $i$ holds $B'_i \sqsubseteq B_i$ and the signature and definition of~$s$ are satisfied.
\end{enumerate}
\end{enumerate}
\luc{introduce the notion of a maximal superblock earlier ???}

@@

\samuel{Angelika: trim this section for repeated information}
Using the dependency graph~(\dependencies) we can reorder the templates such that a template occurs after any template it depends on.
Concretely, the input templates~$\temps$ (see Algorithm~\ref{algo:tcl}) are reordered to agree with the partial ordering imposed by~\dependencies (e.g. \textit{ALLDIFFERENT} before \textit{FOREIGNKEY}).
Considering Algorithm~\ref{algo:tcl}, this step can be seen as preprocessing the input~\temps.
Learning in this order allows templates to use constraints they depend on, as these constraints will have already been learned.
This is exploited in the \generategroups step to speedup the algorithm by reducing the search space.

@@

Aside from finding errors, the system can be extended to deal with noise and the ability to learn soft constraints.
Soft constraints are the (potentially weighted) constraints that hold only on some of the data.
This would extend the approach to new application domains as well as provide more native error detection.

\tias{write limitations: single cons, complete rows/cols only, (what else?) and deal with it as future work}.
\bibliographystyle{plain}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{table*}
\caption{
  Overview of constraint templates implemented in \sname.
  Templates marked with $\dagger$ are \textit{aggregate} templates, the table shows the version for sum but \sname also supports max, min, average, product and count.
  Subgroups in normal font have to be vectors, whereas subgroups in \textbf{bold} may contain more than one vector.
  Templates marked with $*$ are \textit{structural}, i.e. they are not functional and cannot be implemented in most spreadsheet software.
  $\discrete(x)$ is a shortcut for: $\textual(x) \lor \numeric(x)$.  \luc{there are some fancy constraints here. it might be good to say something about them ... like an example of one of the more complex ones in the text ... maybe state what conditional means, what aggregate ... }
}
\label{table:constraints}
  {\centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ \hline \hline
    $\ecalldiff{\sg_x}^*$
      & $\discrete(\sg_x)$

@@

\end{table*}

@@

  \item \CSignature: $\sg_r$ has to be a single vector ($\textit{size}=1$) while $\mathbf{\sg_x}$ can be a block ($\textit{size}>=1$), which can be derived from the use of a normal or \textbf{bold} font.
  Both blocks have to be numeric.
  This constraint is orientation-specific, so it requires that the number of rows in $\mathbf{\sg_x}$ equals the length of $\sg_r$.
  Moreover, we add to the bias that the number of columns to sum over is at least~$2$.

@@

\subsubsection{Redundancies}
\label{sec:form:redundancies}
Depending on the application, some constraints in the solution to the tabular constraint learning problem may be considered \textit{redundant}. This is because constraints may be logically equivalent or may be implied by other constraints, e.g. if you know $\ecperm{B_x}$, $\ecalldiff{B_x}$ is redundant.

@@

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint template all valid argument assignments in two steps:
\begin{enumerate}
\item For each constraint template~$s$, generate all assignments $(B_1, \ldots ,B_n)$ where each $B_i$ is a superblock and the $B_i$ are \textit{compatible} (defined below) with the signature of~$s$. 
\item For each generated assignment $(B_1, \ldots ,B_n)$ in 3a), find all valid constraints $s(B'_1, \ldots, B'_n)$ such that for all $i$ holds $B'_i \sqsubseteq B_i$ and the signature and definition of~$s$ are satisfied.
\end{enumerate}
\end{enumerate}

@@

Using the dependency graph~(\dependencies) we can reorder the templates such that a template occurs after any template it depends on.
Concretely, the input templates~$\temps$ (see Algorithm~\ref{algo:tcl}) are reordered to agree with the partial ordering imposed by~\dependencies (e.g. \textit{ALLDIFFERENT} before \textit{FOREIGNKEY}).
Considering Algorithm~\ref{algo:tcl}, this step can be seen as preprocessing the input~\temps.
Learning in this order allows templates to use constraints they depend on, as these constraints will have already been learned.
This is exploited in the \generategroups step to speedup the algorithm by reducing the search space.

@@

Aside from finding errors, the system can be extended to deal with noise and the ability to learn soft constraints.
Soft constraints are (potentially weighted) constraints that hold only on some of the data.
This would extend the approach to new application domains as well as provide more native error detection.
\bibliographystyle{plain}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
